\cvsection{工作经历}
\begin{cventries}
	  \cventry
	{曼彻斯特大学（The University of Manchester）}
	{研究助理（Research Associate）实习}
	{2018.9 - 2019.3}
	{曼彻斯特}
	{
		\begin{cvitems}
			\item { 主要关注于主流 WoT平台的模型，特别是组件组成机制（composition mechanism）和对应的数据性能（data performance）}
		\end{cvitems}
	}

  \cventry
    {[Nasdaq]国双科技}
    {全职软件工程师}
    {2016.6 - 2017.7}
    {上海}
    {
      \begin{cvitems}
        \item {负责各平台下的数据采集工作（横向组件），包括基于 Web 的用户网页浏览行为数据采集 （JavaScript）、基于智能电视机顶盒或移动应用程序的用户观看行为数据采集（JavaScript，Java）、基于 iOS 或 Android 应用程序的用户使用行为数据采集（Objective-C，Java）}
        \item {作为持续集成（Continuous Integration）系统管理员之一，管理并维护国双持续集成系统 （TeamCity）}
      \end{cvitems}
    }
    
  \cventry
    {上海墨润文化传播有限公司}
    {创业（Startup）, 创始人 \& 技术合伙人}
    {2014.3 - 2016.5}
    { 上海}
    {
      \begin{cvitems}
        \item {作为技术总负责人，领导公司内部技术产品和技术外包项目的研发工作}
        \item {技术产品主要基于 HTML5 + Bootstrap + AngularJS + ASP.NET MVC 5 + Entity Framework 6 (ORM) + Microsoft SQL Server}
      \end{cvitems}
    }
    
  \cventry
    {Judicial Expertise Centre in East China University of Political Science and Law}
    {Intern, Computer Forensics Engineer}
    {Dec. 2013 - Jun. 2014}
    {Shanghai}
    {
      \begin{cvitems}
        \item {Fixed, extracted, and analysed electric evidence on different platforms (Windows, Linux, and iOS), in accordance with regulations of computer judicial expertise and the principles of software systems.}
      \end{cvitems} 
    }
    
  \cventry
    {Shanghai LEVSON Internet Technology Co., Ltd.}
    {Intern, Penetration Test Engineer}
    {Jul. 2013 - Dec. 2013}
    {Shanghai}
    {
      \begin{cvitems}
        \item {Assessed and reinforced the network and application security of clients.}
        \item {Made penetration test and code audit for applications (white box testing).}
        \item {Made safe training for clients and provided solutions when emergencies.}
      \end{cvitems}
    }

\end{cventries}
