\cvsection{Education}
\begin{cventries}
  \cventry
    {M.Sc. in Computer Science (Software Engineering)}
    {UoM (University of Manchester)}
    {Sep. 2017 - Dec. 2018}
    {Manchester}
    {
      \begin{cvitems}
        \item {Research field1 (Distributed systems): utilize the CBSD (Component-based Software Development) theory to qualitatively analyze SOA (especially service composition mechanisms, i.e., orchestration and choreography), Microservice Architecture, RPC frameworks (e.g., EJB, RMI).}
        \item {Research field2 (Internet of Thing): WoT (Web of Things), Fog computing and data performance optimization.}
      \end{cvitems}
    }
    
  \cventry
    {B.Eng. in Computer Science (Internet and Information Security)}
    {ECUPL (East China University of Political Science and Law)}
    {Sep. 2012 - Jun. 2016}
    {Shanghai}
    {
      \begin{cvitems}
        \item {Research field: Information Security, especially Computer Forensics, Electronic Evidence and Data Recovery.}
        \item {As the organiser, organized the Cyber Security Society.}
        \item {Awarded Shanghai Excellent College Student in innovative programmes.}
        \item {Awarded Academic Scholarship of Scientific Research in the school year 2013-2014.}
      \end{cvitems}
    }
    
  \cventry
    {B.A. in Law (Second Degree)}
    {ECUPL (East China University of Political Science and Law)}
    {Sep. 2012 - Jun. 2016}
    {Shanghai}
    {
      \begin{cvitems}
        \item {Mastered a systematic view of the civil law system.}
      \end{cvitems}
    }
\end{cventries}
