\cvsection{Project Experience}
\begin{cventries}
  \cventry
    {Gridsum Holding Inc.}
    {Gridsum Web Dissector / Mobile Dissector/ TV Dissector/ Video Dissector}
    {JavaScript, Objective-C, Java}
    {Jun. 2016 - Jul. 2017}
    {
      \begin{cvitems}
        \item {Contributed to the development of data-collection SDKs for a Web Analytics product (Web Dissector) and mobile App Analytics product (Mobile Dissector).}
        \item {Iterated and improved the video-watching analytics products (TV Dissector and Video Dissector), e.g., solve the memory leak problem, customise the data collection strategies to support the CNTV App (CBox) stably during the Spring Festival.}
      \end{cvitems}
    }
    
  \cventry
    {Shanghai Morun Culture Transmission Co., Ltd.}
    {Realtime Photo-Sharing System}
    {RESTful Web Service}
    {Aug. 2015 - May. 2016}
    {
      \begin{cvitems}
        \item {Led the design and implementation of this technological product, mainly based on HTML5 + Bootstrap + AngularJS + ASP.NET MVC 5 + Entity Framework 6 (ORM) + Microsoft SQL Server, running on the Alibaba Cloud.}
      \end{cvitems}
    }
    
  \cventry
    {East China University of Political Science and Law}
    {WeChat Public Platform Service “ECUPL Teaching Affairs”}
    {RESTful Web Service}
    {Aug. 2015 - Dec. 2015}
    {
      \begin{cvitems}
        \item {Delivered a system which integrates with current teaching administration system, the Moodle system, and the teaching affairs system into a WeChat-based service via ASP.NET Web RESTful API.}
      \end{cvitems}
    }
    
  \cventry
    {Shanghai Pengbei Internet Technology Co., Ltd.}
    {WeChat Public Platform Service Development}
    {RESTful Web Service}
    {Jun.2015 - Aug. 2015}
    {
      \begin{cvitems}
        \item {Took charge of the development of a food-delivered system based on the WeChat Public Platform.}
      \end{cvitems}
    }
    
  \cventry
    {East China University of Political Science and Law}
    {Teaching Management Information Inquiry System}
    {WPF (MVVM)}
    {Apr. 2015 - Jul. 2015}
    {
      \begin{cvitems}
        \item {Directed and achieved a client-server system used for touch-screen machines, based on Microsoft WPF (MVVM Framework).}
      \end{cvitems}
    }
    
  \cventry
    {Pansafe Software (Shanghai) Co., Ltd.}
    {Email Authenticity Identification System}
    {WPF (MVVM)}
    {Sep. 2014 - Jan. 2015}
    {
      \begin{cvitems}
        \item {Researched validation rules in accordance with Request for Comments (RFCs) and developed the system which identifies the authenticity of emails based on Naive Bayesian.}
      \end{cvitems}
    }
\end{cventries}
