\cvsection{Work Experience}
\begin{cventries}
	  \cventry
	{The University of Manchester}
	{Intern, Research Associate}
	{Sep. 2018 - Mar. 2019}
	{Manchester}
	{
		\begin{cvitems}
			\item {Mainly focused on the models of mainstream Web of Things platforms, especially the underlying composition mechanisms and their corresponding data performance.}
		\end{cvitems}
	}

  \cventry
    {Gridsum Holding Inc.}
    {Full-time, Software Engineer (Data collection team)}
    {Jun. 2016 - Jul. 2017}
    {Shanghai}
    {
      \begin{cvitems}
        \item {Contributed to the development of data-collection SDKs to collect user behaviours in various scenarios, including Web-based pages (vanilla JavaScript), TV set-top boxes (vanilla JavaScript, Java), iOS apps (Objective-C), and Android apps (Java).}
        \item {As a \textit{Continuous-Integration} system (TeamCity) admin, took part in managing and maintaining the Gridsum CI system.}
      \end{cvitems}
    }
    
  \cventry
    {Shanghai Morun Culture Transmission Co., Ltd.}
    {Startup, Co-founder \& Lead Software Engineer}
    {Mar. 2014 - May 2016}
    {Shanghai}
    {
      \begin{cvitems}
        \item {Organized the whole life cycle of the development of software products and maintained IT infrastructure.}
      \end{cvitems}
    }
    
  \cventry
    {Judicial Expertise Centre in East China University of Political Science and Law}
    {Intern, Computer Forensics Engineer}
    {Dec. 2013 - Jun. 2014}
    {Shanghai}
    {
      \begin{cvitems}
        \item {Fixed, extracted, and analysed electric evidence on different platforms (Windows, Linux, and iOS), in accordance with regulations of computer judicial expertise and the principles of software systems.}
      \end{cvitems} 
    }
    
  \cventry
    {Shanghai LEVSON Internet Technology Co., Ltd.}
    {Intern, Penetration Test Engineer}
    {Jul. 2013 - Dec. 2013}
    {Shanghai}
    {
      \begin{cvitems}
        \item {Assessed and reinforced the network and application security of clients.}
        \item {Made penetration test and code audit for applications (white box testing).}
        \item {Made safe training for clients and provided solutions when emergencies.}
      \end{cvitems}
    }

\end{cventries}
